Kindly Bent to Free Us

### 2019-11-13 kindly/lang.tex
Minor layout changes.

@@

\begin{figure*}[!tb]
  \centering
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
\end{figure*}

@@

Kinds form a lattice with an ordering that implements two principles
(see \cref{sdtyp:lattice}). First, unrestricted values may be used
where affine ones are expected and affine ones are less restricted
than linear ones as reflected in \TirName{Lat-UA} and \TirName{Lat-AL}.
Second, values usable at level $n$ may be used at any more deeply
nested level $n'$ (where $n\le\infty$ for any $n$) as defined in the \TirName{Lat-X-Level} axioms.

@@

\begin{figure*}[tp]
  \input{infer/lattice}
  \caption{Lattice ordering -- $k \lk_\Lat k'$}
  \label{sdtyp:lattice}
\end{figure*}

@@

A storable $w$ is a particular object that can be stored. There are five
kinds of storable. A poly closure represents a polymorphic
function. It consists of an environment and the components of an
elaborated abstraction. Similarly, a closure represents a monomorphic
function and it elides kind variables and the constraint. A pair
consists of a kind and two results. A resource is just an indirection
to another result and the $\blob $ fills a released location.

>>>>

\begin{figure}[!tb]
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
\end{figure}

@@

@@

Kinds form a lattice with an ordering that implements two principles
(see \cref{sdtyp:lattice}). First, unrestricted values may be used
where affine ones are expected and affine ones are less restricted
than linear ones as reflected in \TirName{Lat-UAL}.
Second, values usable at level $n$ may be used at any more deeply
nested level $n'$ (where $n\le\infty$ for any $n$) as defined in the \TirName{Lat-Level} axioms.

@@

\begin{figure}[tp]
  \input{infer/lattice}
  \caption{Lattice ordering -- $k \lk_\Lat k'$}
  \label{sdtyp:lattice}
\end{figure}

@@

A storable $w$ is a particular object that can be stored. There are five
kinds of storable. A poly closure represents a polymorphic
function. It consists of an environment and the components of an
elaborated abstraction. Similarly, a closure represents a monomorphic
function and it elides kind variables and the constraint. A pair
consists of a kind and two results. A resource is just an indirection
to another result and the $\StFreed$ fills a released location.
